\demes: a Python package for pain-free specification of complex demography

### 2020-11-11 paper.tex
input model code from yaml

\begin{itemize}
\item Short description of YAML language and why it's appropriate here
\item General overview (1 paragraph) of defining demography in YAML
\item A generic, commonly used, simple demographic model for illustration (e.g. IM)
\end{itemize}

\begin{code}
\label{code:im_model}
\captionof{listing}{An IM model.}
\begin{minted}[linenos,numbersep=5pt]{yaml}
description: A two-population isolation-with-migration model.
time_units: generations
demes:
  ancestral:
    description: The ancestral deme that splits into two child demes.
    initial_size: 5000
    end_time: 2000
  deme1:
    description: The first child deme.
    ancestors: ancestral
    initial_size: 1000
    final_size: 10000
  deme2:
    description: The second child deme.
    ancestors: ancestral
    initial_size: 2000
    final_size: 8000
migrations:
  symmetric:
  - demes: deme1, deme2
    rate: 1e-4
\end{minted}
\end{code}

>>>>

\begin{itemize}
\item Short description of YAML language and why it's appropriate here
\item General overview (1 paragraph) of defining demography in YAML
\item A generic, commonly used, simple demographic model for illustration (e.g.
  an IM in Model~\ref{code:im_model})
\end{itemize}

\begin{code}
\captionof{listing}{An IM model.}
\begin{tcolorbox}
\inputminted[linenos,numbersep=5pt]{yaml}{models/IM.yaml}
\end{tcolorbox}
\label{code:im_model}
\end{code}
